
\cvsection{Publications}

Peer-reviewed

\begin{itemize}
    \item Deep Text Prior: Weakly Supervised Learning for Assertion Classification (ICANN 2019)
    \item Active Learning with Deep Pre-trained Models for Sequence Tagging of Clinical and Biomedical Texts (BIBM 2019)
    \item Topic evolution modeling using lda2vec (OCUPAI 2019\footnotemark)
\end{itemize}

Not formally reviewed:

\begin{itemize}
    \item The Promise and Perils of Sleeping at Hackathons\footnotemark
    \item Opening the Black Box of Deep Neural Networks with more information \footnotemark
\end{itemize}

\cvsection{SKILLS}

\begin{itemize}
    \item Strong mathematical background. Calculus, optimization, numerical linear algebra.
    \item Deep Learning: ConvNets, RNNs, Attention, GANs. Pytorch and Tensorflow.
    \item Statistics. Bayesian and Neurobayesian methods
    \item Natural Language Processing. Language Models, Information Extraction, Image Captioning.
    \item Efficient algorithms and data structures
    \item C, C++, C\#, Java, Clojure, Python, JavaScript, bash, PHP :(
    \item x86 architecture: paging, stack, interrupts, assembly language
    \item Databases: Not-only-SQL.
    \item Project management methodologies. Scrum.
    \item Requirements management, e.g. developing user stories. Working with non-technical clients.
    \item Russian-English bilingual. Intermediate French.
\end{itemize}

\cvsection{Teaching}
\begin{itemize}
    \item Course author and instructor @ \emph{Functional Programming with Clojure}. Skoltech 2018, 2019. 
    \item Course author and instructor @ \emph{Introduction to Artificial Humour}. Skoltech 2019.
    \item Course instructor @ \emph{Computer Vision}. Netology 2019.
    \item Mentor @ \emph{Natural Language Processing}. Netology 2019.
    \item Mentor @ \emph{Neurohackathon 2018}. Medical image segmentation for Multiple Sclerosis.
\end{itemize}

\cvsection{Hackathons}

\begin{itemize}
    \item Junction. Helsinki 2018 \& 2019
    \item HackUPC. Barcelona 2017
    \item The Room of the Future. Budapest 2018 \faTrophy
    \item Microsoft ImagineCup Hackathon 2017
\end{itemize}